---
title: "Meta-analysis of avian responses and butterfly eyespots"
author: "**Mizuno et al.**"
date: "`r Sys.Date()`"
format: 
  html:
    toc: true
    toc-location: left
    toc-depth: 3
    toc-float: true
    toc-title: "**Contents**"
    output-file: "index.html"
    embed-resources: true
    code-fold: true
    code-tools: true
    number-sections: true
    #bibliography: ./bib/ref.bib
    fontsize: "12"
    max-width: "10"
    code-overflow: wrap
    df_print: paged
    theme: minty
    code-line-numbers: false　　　
crossref: 
  fig-title: Figure     # (default is "Figure")
  tbl-title: Table     # (default is "Table")
  title-delim:  —     # (default is ":")
  fig-prefix: Fig.   # (default is "Figure")
  tbl-prefix: Table.    # (default is "Table")
editor_options: 
  chunk_output_type: console
execute:
  warning: false
  message: false
  tidy: true
  #cache: true
---

# Setting ups

## Load packages and custum function
Load packages and custum function.
Custom function is used for calculating effect size (lnRR) and its variance from raw data.

```{r}

pacman::p_load(ape,
               GoodmanKruskal,
               DT,
               dtplyr,
               ggokabeito,
               ggcorrplot,
               here, 
               knitr,
               tidyverse,
               patchwork,
               metafor,
               miWQS,
               multcomp,
               orchaRd,
               parallel)

# function for calculating effect size (lnRR)
effect_lnRR <- function(dt) {
  # replace 0 in "C_mean", "T_sd", "C_sd", "C_proportion" with each minimum values
  # if proportion too extreme value, replace minimum value (only "T_proportion")

  dt <- dt %>%
  mutate(
    C_mean = ifelse(C_mean == 0, 0.04, C_mean),
    T_sd = ifelse(T_sd == 0, 0.01, T_sd),
    C_sd = ifelse(C_sd == 0, 0.05, C_sd),
    C_proportion = ifelse(C_proportion == 0, 0.01, C_proportion),
    T_proportion = ifelse(T_proportion < 0.01, 0.01, T_proportion),
    T_proportion = ifelse(T_proportion == 1, 0.9, T_proportion)
  )
    
  # copy dataset for adding effect size and its variation (lnRR /lnRR_var) column
  dt1 <- dt %>%
    mutate(
      lnRR = NA,
      lnRR_var = NA
    )

  for (i in seq_len(nrow(dt1))) {
    Tn <- dt1$Tn[i]
    Cn <- dt1$Cn[i]
    T_mean <- dt1$T_mean[i]
    C_mean <- dt1$C_mean[i]
    T_proportion <- dt1$T_proportion[i]
    C_proportion <- dt1$C_proportion[i]
    T_sd <- dt1$T_sd[i]
    C_sd <- dt1$C_sd[i]
    Response <- dt1$Response[i]
    Measure <- dt1$Measure[i]
    Study_design <- dt1$Study_design[i]
    Direction <- dt1$Direction[i]

    # continuous data - using escalc() (metafor package)
    if (Response == "continuous" & Study_design == "independent") {

      effect <- escalc(
        measure = "ROM",
        n1i = Tn, n2i = Cn,
        m1i = T_mean, m2 = C_mean,
        sd1i = T_sd, sd2i = C_sd,
        var.names = c("lnRR", "lnRR_var")
      )

      dt1$lnRR[i] <- effect$lnRR
      dt1$lnRR_var[i] <- effect$lnRR_var
    } else if (Response == "continuous" & Study_design == "dependent") {

      effect <- escalc(
        measure = "ROMC",
        ni = (Tn + Cn) / 2,
        m1i = T_mean, m2 = C_mean,
        sd1i = T_sd, sd2i = C_sd,
        ri = 0.5,
        var.names = c("lnRR", "lnRR_var")
      )

      dt1$lnRR[i] <- effect$lnRR
      dt1$lnRR_var[i] <- effect$lnRR_var
    }

    # proportion data (no sd values)
    else if (Response == "proportion1" & Study_design == "independent") {
      
    T_proportion <- replace(
        T_proportion, Direction == "Decrease",
        (1 - T_proportion[Direction == "Decrease"])
      )
      C_proportion <- replace(
        C_proportion, Direction == "Decrease",
        (1 - C_proportion[Direction == "Decrease"])
      )

      # transform proportion value
      asin_trans <- function(proportion) {
        trans <- asin(sqrt(proportion))
        trans
      }

      T_proportion <- asin_trans(T_proportion)
      C_proportion <- asin_trans(C_proportion)

      # calculate lnRR and lnRR variance
      lnRR_pro1 <- log(T_proportion / C_proportion)
      lnRR_var_pro1 <- (1 / sqrt(8))^2 * (1 / (T_proportion^2 * Tn) +
        1 / (C_proportion^2 * Cn))

      dt1$lnRR[i] <- lnRR_pro1
      dt1$lnRR_var[i] <- lnRR_var_pro1

    } else if (Response == "proportion1" & Study_design == "dependent") {
      
      T_proportion <- replace(
        T_proportion, Direction == "Decrease",
        (1 - T_proportion[Direction == "Decrease"])
      )
      C_proportion <- replace(
        C_proportion, Direction == "Decrease",
        (1 - C_proportion[Direction == "Decrease"])
      )

      # transform proportion value
      asin_trans <- function(proportion) {
        trans <- asin(sqrt(proportion))
        trans
      }

      T_proportion <- asin_trans(T_proportion)
      C_proportion <- asin_trans(C_proportion)

      # calculate lnRR and lnRR variance
      lnRR_pro1 <- log(T_proportion / C_proportion)
      lnRR_var_pro1 <- (1 / sqrt(8))^2 * (1 / (T_proportion^2 * Tn) +
        1 / (C_proportion^2 * Cn)) -
        2 * 0.5 * sqrt((1 / sqrt(8))^2 * (1 / (T_proportion^2 * Tn))) *
          sqrt((1 / sqrt(8))^2 * (1 / (C_proportion^2 * Cn)))

      dt1$lnRR[i] <- lnRR_pro1
      dt1$lnRR_var[i] <- lnRR_var_pro1
    }

    # proportion data (exist sd values)
    else if (Response == "proportion2" & Study_design == "independent") {
      
      T_proportion <- replace(
        T_proportion, Direction == "Decrease",
        (1 - T_proportion[Direction == "Decrease"])
      )
      C_proportion <- replace(
        C_proportion, Direction == "Decrease",
        (1 - C_proportion[Direction == "Decrease"])
      )
      
      # transform proportion mean value
      asin_trans <- function(proportion) {
        trans <- asin(sqrt(proportion))
        trans
      }

      T_SD <- sqrt(T_sd^2 / (4 * (T_proportion) * (1 - (T_proportion))))
      C_SD <- sqrt(C_sd^2 / (4 * (C_proportion) * (1 - (C_proportion))))

      T_proportion <- asin_trans(T_proportion)
      C_proportion <- asin_trans(C_proportion)

      # calculate lnRR and lnRR variance
      lnRR_pro2 <- log(T_proportion / C_proportion)
      lnRR_var_pro2 <- (T_SD)^2 * (1 / (T_proportion^2 * Tn)) +
        (C_SD)^2 * (1 / (C_proportion^2 * Cn))

      dt1$lnRR[i] <- lnRR_pro2
      dt1$lnRR_var[i] <- lnRR_var_pro2

    } else if (Response == "proportion2" & Study_design == "dependent") {
      
      T_proportion <- replace(
        T_proportion, Direction == "Decrease",
        (1 - T_proportion[Direction == "Decrease"])
      )
      C_proportion <- replace(
        C_proportion, Direction == "Decrease",
        (1 - C_proportion[Direction == "Decrease"])
      )
      
      # transform proportion mean value
      asin_trans <- function(proportion) {
        trans <- asin(sqrt(proportion))
        trans
      }

      T_SD <- sqrt(T_sd^2 / (4 * (T_proportion) * (1 - (T_proportion))))
      C_SD <- sqrt(C_sd^2 / (4 * (C_proportion) * (1 - (C_proportion))))

      T_proportion <- asin_trans(T_proportion)
      C_proportion <- asin_trans(C_proportion)

      # calculate lnRR and lnRR variance
      lnRR_pro2 <- log(T_proportion / C_proportion)
      lnRR_var_pro2 <- (T_SD)^2 * (1 / (T_proportion^2 * Tn)) +
        (C_SD)^2 * (1 / (C_proportion^2 * Cn)) -
        2 * 0.5 * sqrt((T_SD)^2 * (1 / (T_proportion^2 * Tn))) *
          sqrt((C_SD)^2 * (1 / (C_proportion^2 * Cn)))

      dt1$lnRR[i] <- lnRR_pro2
      dt1$lnRR_var[i] <- lnRR_var_pro2
    }
  }

  return(dt1)
}
```

## Prepare datasets for analysis

::: {.panel-tabset}

### Read datasets and phylogeny
First, we used a predator dataset to check whether we need to consider phylogeney. If so, we will use predator and prey datasets for following meta-analysis.

```{r}
#| label: tbl-dataset
#| tbl-cap: "Predator dataset"

dat_all <-  read.csv(here("data/all_21092023.csv"), header = T, fileEncoding = "CP932")
dat_pred <- filter(dat_all, Dataset == "predator")
dat_prey <- filter(dat_all, Dataset == "prey")

datatable(dat_all, caption = "all dataset", options = list(pageLength = 10, scrollX = TRUE))
```
**Table 1 - Predator + prey datasets**


```{r}
#| label: fig-tree
#| fig-cap: "Phylogenetic tree of bird species"

trees <- read.nexus(here("data/bird_phy.nex"))
plot(trees[1])
```



### Calculate lnRR and lnRR variance and prepare datasets for analysis
```{r}
# predator dataset
dt_pred <- effect_lnRR(dat_pred)
dt_pred$Obs_ID <- 1:nrow(dt_pred)
dt_pred$Log_diameter <- log(dt_pred$Diameter_pattern)
dt_pred$Log_area <- log(dt_pred$Area_pattern)
dt_pred$Log_background <- log(dt_pred$Area_background)

# prey dataset
dt_prey <- effect_lnRR(dat_prey)
dt_prey$Obs_ID <- 1:nrow(dt_prey)
dt_prey$Log_diameter <- log(dt_prey$Diameter_pattern)
dt_prey$Log_area <- log(dt_prey$Area_pattern)
dt_prey$Log_background <- log(dt_prey$Area_background)

# all dataset
dt_all <- effect_lnRR(dat_all)
dt_all$Obs_ID <- 1:nrow(dt_all)
dt_all$Log_diameter <- log(dt_all$Diameter_pattern)
dt_all$Log_area <- log(dt_all$Area_pattern)
dt_all$Log_background <- log(dt_all$Area_background)

hist(dt_all$lnRR)
hist(dt_all$lnRR_var)

# use vcalc to calculate variance-covariance matrix
VCV_pred <- vcalc(vi = lnRR_var, 
                  cluster = Cohort_ID, 
                  subgroup = Obs_ID, 
                  data = dt_pred)

VCV_prey <- vcalc(vi = lnRR_var, 
                  cluster = Cohort_ID, 
                  subgroup = Obs_ID, 
                  data = dt_prey)

VCV <- vcalc(vi = lnRR_var, 
             cluster = Cohort_ID,
             obs = Obs_ID,
             rho = 0.5,
             data = dt_all)

dt_pred <- dt_pred %>%
  mutate_if(is.character, as.factor)
dt_prey <- dt_prey %>%
  mutate_if(is.character, as.factor)
dt_all <- dt_all %>%
  mutate_if(is.character, as.factor)

summary(dt_pred)
summary(dt_prey)
summary(dt_all)

```


### Final dataset for meta-analysis
I cannot attach the caption to `datatable()` format table. I need to use `kable()` format table?
```{r}
#| label: all dataset
#| tbl-cap: "Our datasets included predator and prey datasets"

datatable(dt_all, caption = "Dataset for meta-analysis", 
          options = list(pageLength = 10, scrollX = TRUE))
```
**Table 2 - Dataset for meta-analysis**


### Check phylogenetic relatedness
If phylogeny do not explain heterogeniety much, we will not need to consider it and the two datasets can be merged.

We used meta-analytical models to calculate total I2 (a measure of heterogeneity not caused by sampling error; Higgins. et al., 2003) and the partial I2 explained by each random factor.

Based on this, we need not to consider phylogenetic relatedness from our meta-regressions as this random factor did not explain much of the heterogeneity between effect sizes (partial I2 < 0.001%), then we can combine two datasets (predator and prey) for meta-analysis.

```{r}
#| eval: false

phy_model <- function(cor_tree = vcv_tree){
            model <- rma.mv(yi = lnRR,
                            V = VCV_pred,
                            random = list(~1 | Study_ID,
                                          ~1 | Shared_control_ID,
                                          ~1 | Cohort_ID,
                                          ~1 | Obs_ID,
                                          ~1 | Bird_species,
                                          ~1 | Phylogeny),
                            R = list(Phylogeny = cor_tree),
                            test = "t",
                            method = "REML",
                            sparse = TRUE,
                            data = dat_pred)
  model
}

tree_50 <- trees[1:50]
vcv_tree_50 <- map(tree_50, ~vcv(.x, corr = TRUE))

# Run multiple meta-analyses with 50 different trees and obtain the combined result

ma_50 <- mclapply(vcv_tree_50, phy_model, mc.cores = 8) 
```

```{r}
#| results: hide

ma_50 <- readRDS(here("Rdata", "ma_50.RDS"))

# combining the results
est_50 <- map_dbl(ma_50, ~ .x$b[[1]])
se_50 <-  map_dbl(ma_50, ~ .x$se)
df_50 <- c(rbind(est_50, se_50))

# creating an array required by pool.mi
my_array <- array(df_50, dim = c(1, 2, 50))

com_res <- round(pool.mi(my_array), 4)
```

```{r}

knitr::kable(com_res, caption = "Combined result of 50 phylogenetic trees")

sigma2_mod <- do.call(rbind, lapply(ma_50, function(x) x$sigma2))
sigma2_mod <- data.frame(sigma2_mod)

colnames(sigma2_mod) <- c("sigma^2.1_Study_ID", "sigma^2.2_SharedControl_ID", 
                          "sigma^2.3_Cohort_ID", "sigma^2.4_Obs_ID", 
                          "sigma^2.5_BirdSpecies", "sigma^2.6_Phylogeny")

sigma2_mod <- round(colMeans(sigma2_mod), 4)

knitr::kable(sigma2_mod, caption = "Average variance components")

```

::: callout-note

## We got 1000 phylogenetic trees from [BirdTree.org](https://birdtree.org)

Only 50 trees are used as in [Nakagawa & Villemereuil (2019)](https://doi.org/10.1093/sysbio/syy089)

:::
:::
# Meta-analysis - predator dataset

We used meta-analytical models to calculate total I2 (a measure of heterogeneity not caused by sampling error; Higgins. et al., 2003) and the partial I2 explained by each random factor.

::: callout-note
## Which random effects remove in our models?

We can remove _Study_ID_
:::

```{r}

ma_pred <- rma.mv(yi = lnRR,
                  V = VCV_pred, 
                  random = list(~1 | Study_ID,
                                ~1 | Shared_control_ID,
                                ~1 | Cohort_ID,
                                ~1 | Obs_ID),
                  test = "t",
                  method = "REML", 
                  sparse = TRUE,
                  data = dt_pred)

summary(ma_pred)

pred_i2 <- round(i2_ml(ma_pred), 4)

pred_r2 <- round(r2_ml(ma_pred), 4)
```

```{r}
#| echo: false
pred_t_i2 <- t(pred_i2)
pred_t_r2 <- t(pred_r2)
knitr::kable(pred_t_i2)
knitr::kable(pred_t_r2)
```
**Table 3 - Heterogeneity of effect size**

```{r}
#| label: fig-ma_pred
#| fig-cap: "Estimates of overpred effect size and 95% confidence intervals"
#| fig-cap-location: bottom

orchard_plot(ma_pred,
              group = "Study_ID",
              xlab = "log response ratio (lnRR)", 
              angle = 45) + 
              scale_x_discrete(labels = c("Overall effect")) + 
              scale_colour_okabe_ito()+
              scale_fill_okabe_ito()

```

## Meta-regressions: uni-moderator - predetor dataset

:::{.panel-tabset}

### Pattern type
Eyespot vs. conspicuous patterns - Is there significant difference of effect size between two patterns?

```{r}

#normal model
pred_mr_eyespot <- rma.mv(yi = lnRR,
                    V = VCV_pred, 
                    mods = ~ Treatment_stimulus,
                    random = list(~1 | Shared_control_ID,
                                ~1 | Cohort_ID,
                                ~1 | Obs_ID),
                    test = "t",
                    method = "REML", 
                    sparse = TRUE,
                    data = dt_pred)

summary(pred_mr_eyespot)

pred_r2_1 <- round(r2_ml(pred_mr_eyespot), 4)
```

```{r}
#| echo: false


pred_t_r2_1 <- t(pred_r2_1)
knitr::kable(pred_t_r2_1)  
```
**Table XX. Model goodness-of-fit**


```{r}
#| label: fig-eyespot_pred
#| fig-cap: "Eyespot vs. conspicuous patterns"

orchard_plot(pred_mr_eyespot,
            mod = "Treatment_stimulus",
            group = "Study_ID",
            xlab = "log response ratio (lnRR)",
            angle = 45) + 
            scale_colour_okabe_ito(order = 2:3)+
            scale_fill_okabe_ito(order = 2:3)

```


```{r}

# intercept-removed model
pred_mr_eyespot1 <- rma.mv(yi = lnRR,
                      V = VCV_pred, 
                      mods = ~ Treatment_stimulus -1,
                      random = list(~1 | Shared_control_ID,
                                ~1 | Cohort_ID,
                                ~1 | Obs_ID),
                                test = "t",
                      method = "REML", 
                      sparse = TRUE,
                      data = dt_pred)

summary(pred_mr_eyespot1)

```

### Pattern diameter (mm) 

```{r}
#| label: fig-diameter_pred
#| fig-cap: "Effect size and pattern diameter"

pred_mr_diameter <- rma.mv(yi = lnRR,
                      V = VCV_pred, 
                      mods = ~ Log_diameter,
                      random = list(~1 | Shared_control_ID,
                                ~1 | Cohort_ID,
                                ~1 | Obs_ID),
                      test = "t",
                      method = "REML", 
                      sparse = TRUE,
                      data = dt_pred)

summary(pred_mr_diameter)


pred_r2_2 <- round(r2_ml(pred_mr_diameter), 4)
```

```{r}
#| echo: false


pred_t_r2_2 <- t(pred_r2_2)
knitr::kable(pred_t_r2_2)  
```
**Table XX. Model goodness-of-fit**

```{r}

bubble_plot(pred_mr_diameter,
            mod = "Log_diameter",
            group = "Study_ID",
            xlab = "Log-transformed diameter")

```

### Pattern area (mm²)

```{r}
#| label: fig-area_pred
#| fig-cap: "Effect size and pattern area"

pred_mr_area <- rma.mv(yi = lnRR,
                  V = VCV_pred, 
                  mods = ~ Log_area,
                  random = list(~1 | Shared_control_ID,
                                ~1 | Cohort_ID,
                                ~1 | Obs_ID),
                  test = "t",
                  method = "REML", 
                  sparse = TRUE,
                  data = dt_pred)

summary(pred_mr_area)

pred_r2_3 <- round(r2_ml(pred_mr_area), 4)
```

```{r}
#| echo: false

pred_t_r2_3 <- t(pred_r2_3)
knitr::kable(pred_t_r2_3)  
```
**Table XX. Model goodness-of-fit**

```{r}

bubble_plot(pred_mr_area,
            mod = "Log_area",
            group = "Study_ID",
            xlab = "Log-transformed area")

```

### Pattern number

```{r}
#| label: fig-number_pred
#| fig-cap: "Effect size and number of patterns"

pred_mr_num <- rma.mv(yi = lnRR,
                  V = VCV_pred,
                  mods = ~ Number_pattern,
                  random = list(~1 | Shared_control_ID,
                                ~1 | Cohort_ID,
                                ~1 |Obs_ID),                      
                      test = "t",
                      method = "REML",
                      sparse = TRUE,
                      data = dt_pred)

summary(pred_mr_num)

pred_r2_4 <- round(r2_ml(pred_mr_num), 4)
```

```{r}
#| echo: false

pred_t_r2_4 <- t(pred_r2_4)
knitr::kable(pred_t_r2_4)  
```

**Table XX. Model goodness-of-fit**
  
```{r}

bubble_plot(pred_mr_num,
            mod = "Number_pattern",
            group = "Study_ID",
            xlab = "Number of patterns") 

```


### Prey material type
Our dataset includes two material types of prey: live and artificial. Is there significant difference of effect size between two stimuli?
```{r}
#| label: fig-stimuli_pred
#| fig-cap: "Effect size and prey type - real vs. artificial"

# normal model
pred_mr_prey_type <- rma.mv(yi = lnRR,
                  V = VCV_pred, 
                  mods = ~ Type_prey,
                  random = list(~1 | Shared_control_ID,
                                ~1 | Cohort_ID,
                                ~1 | Obs_ID), 
                  test = "t",
                  method = "REML", 
                  sparse = TRUE,
                  data = dt_pred)

summary(pred_mr_prey_type)

pred_r2_5 <- round(r2_ml(pred_mr_prey_type), 4)

```

```{r}
#| echo: false

pred_t_r2_5 <- t(pred_r2_5)
knitr::kable(pred_t_r2_5)

```
**Table XX. Model goodness-of-fit**

```{r}

orchard_plot(pred_mr_prey_type,
              mod = "Type_prey",
              group = "Study_ID",
              xlab = "Type of prey",
              angle = 45) +
            scale_colour_okabe_ito(order = 4:5)+
            scale_fill_okabe_ito(order = 4:5)


# intercept-removed model
pred_mr_prey_type1 <- rma.mv(yi = lnRR,
                            V = VCV_pred, 
                            mods = ~ Type_prey -1,
                            random = list(~1 | Shared_control_ID,
                                ~1 | Cohort_ID,
                                ~1 | Obs_ID), 
                            test = "t",
                            method = "REML", 
                            sparse = TRUE,
                            data = dt_pred)

summary(pred_mr_prey_type1)
```

### Prey shape type
Our dataset includes 4 types of prey type: real butterfly, abstract butterfly, abstract caterpillar, and abstract prey. Is there significant difference of effect size between two stimuli?

```{r}

pred_mr_prey_shape <- rma.mv(yi = lnRR,
                        V = VCV_pred, 
                        mods = ~ Shape_prey -1,
                        random = list(~1 | Shared_control_ID,
                                ~1 | Cohort_ID,
                                ~1 | Obs_ID),,
                                      test = "t",
                                      method = "REML", 
                                      sparse = TRUE,
                                      data = dt_pred)

summary(pred_mr_prey_shape)

pred_r2_6 <- round(r2_ml(pred_mr_prey_shape), 4)
```

```{r}
#| echo: false

pred_t_r2_6 <- t(pred_r2_6)
knitr::kable(pred_t_r2_6)  
```
**Table XX. Model goodness-of-fit**

```{r}
#| label: fig-shape_pred
#| fig-cap: "Effect size and prey shape"

orchard_plot(pred_mr_prey_shape,
              mod = "Shape_prey",
              group = "Study_ID",
              xlab = "Shape of prey",
              angle = 45) +
              scale_colour_okabe_ito(order = 6:9)+
              scale_fill_okabe_ito(order = 6:9)

```

:::

## Correlation visualisation and choose moderators for multi-moderator meta-regression in predator dataset
Before we run multi-moderator meta-regressions, we need to consider the correlation between moderators.
Area, diameter and background seem to be correlated. We visualised the correlation between these variables.

:::{.panel-tabset}

### Visualisation of correlation

```{r}
#| label: fig-cor-continuous_pred
#| fig-cap: "Correlation between coninuous moderators"

# correlation between continuous variables
pred_corr_cont <- round(cor(dt_pred[, c("Diameter_pattern", "Area_pattern", "Number_pattern", "Area_background")]),2)

pred_p1 <- ggcorrplot(pred_corr_cont, hc.order = TRUE, lab = TRUE, outline.col = "white", colors = c("#6D9EC1", "white", "#E46726"), title = "(a) Continuous variables")

pred_corr_cont_log <- round(cor(dt_pred[, c("Log_diameter", "Log_area", "Number_pattern", "Log_background")]),2)

pred_p2 <- ggcorrplot(pred_corr_cont_log, hc.order = TRUE, lab = TRUE, outline.col = "white", colors = c("#6D9EC1", "white", "#E46726"), title = "(b) Log-transormed continuous variables")

pred_p1 + pred_p2 +plot_layout(guides = 'collect')
```

```{r}
#| label: fig-cor-categorical_pred
#| fig-cap: "Correlation between categorical variables"

summary(dt_pred$Treatment_stimulus)
pred_dat1 <- dt_pred %>%
  dplyr::select("Treatment_stimulus", "Type_prey", "Shape_prey")

pred_corr_cat <- GKtauDataframe(pred_dat1)
plot(pred_corr_cat)

```
We should not include "Shape_prey" and "Type_prey" in the model at the same time. Because they are correlated.

### Choose moderators
We used model R2 values to find better model and modelator VIF values to check multicollinearity between moderators. 
Higher R2 indicates better model and VIF > 2 indicates multicollinearity. 

#### R2
```{r}

pred_r2_area <- rma.mv(yi = lnRR,
                  V = VCV_pred,
                  mods = ~ Log_area + Number_pattern,
                  random = list(~1 | Shared_control_ID,
                                ~1 | Cohort_ID,
                                ~1 | Obs_ID),
                  test = "t",
                  method = "REML",
                  sparse = TRUE,
                  data = dt_pred)

pred_r2_diameter <- rma.mv(yi = lnRR,
                      V = VCV_pred,
                      mods = ~ Log_diameter + Number_pattern,
                      random = list(~1 | Shared_control_ID,
                                ~1 | Cohort_ID,
                                ~1 | Obs_ID),
                      test = "t",
                      method = "REML",
                      sparse = TRUE,
                      data = dt_pred)

# check r2 values
r2_ml(pred_r2_area)
r2_ml(pred_r2_diameter)

```
It seems **area** is a better predictor than **diameter** .

:::

## Meta-regressions: multi-moderator

:::{.panel-tabset}

### All potential moderators (full model)
Include all moderators in the model.

```{r}

pred_mr_all <- rma.mv(yi = lnRR,
                V = VCV_pred, 
                mods = ~ Treatment_stimulus + Log_area 
                + Number_pattern + Type_prey,
                random = list(~1 | Shared_control_ID,
                                ~1 | Cohort_ID,
                                ~1 | Obs_ID),
                test = "t",
                method = "REML", 
                sparse = TRUE,
                data = dt_pred)

summary(pred_mr_all)

r2_ml(pred_mr_all)
```

### Moderators associated with conspicuousness
Only include moderators related to conspicuousness (pattern area and number of patterns) in the model.

```{r}

pred_mr_cons <- rma.mv(yi = lnRR,
                V = VCV_pred, 
                mods = ~ Log_area + Number_pattern,
                random = list(~1 | Shared_control_ID,
                              ~1 | Cohort_ID,
                              ~1 | Obs_ID),
                test = "t",
                method = "REML", 
                sparse = TRUE,
                data = dt_pred)

summary(pred_mr_cons)

r2_ml(pred_mr_cons)

bubble_plot(pred_mr_cons,
            mod = "Log_area",
            group = "Study_ID",
            xlab = "Log-transformed area")

```


```{r}
pred_mr_cons_1 <- rma.mv(yi = lnRR,
                V = VCV_pred, 
                mods = ~ Log_area + Number_pattern + Treatment_stimulus,
                random = list(~1 | Shared_control_ID,
                                ~1 | Cohort_ID,
                                ~1 | Obs_ID),
                test = "t",
                method = "REML", 
                sparse = TRUE,
                data = dt_pred)

summary(pred_mr_cons_1)

r2_ml(pred_mr_cons_1)

```

### Moderators associated with prey in predator dataset
```{r}
pred_mr_pre <- rma.mv(yi = lnRR,
                V = VCV_pred, 
                mods = ~ Treatment_stimulus + Type_prey,
                random = list(~1 | Shared_control_ID,
                                ~1 | Cohort_ID,
                                ~1 | Obs_ID),
                test = "t",
                method = "REML", 
                sparse = TRUE,
                data = dt_pred)

summary(pred_mr_pre)

r2_ml(pred_mr_pre)
```
:::

## Publication bias

:::{.panel-tabset}

### Funnel plot

```{r}
#| layout-ncol: 2
#| label: fig-funnel_pred
#| fig-cap: "Funnel plot of effect size and its standard error"
#| fig-subcap: 
#|   - "Effect size and its standard error"
#|   - "Effect size and its inverse standard error"

# funnel plot - standard error
funnel(ma_pred, yaxis = "sei", 
      xlab = "Standarised residuals",
      ylab = "Precision (inverse of SE)" )

# funnel plot - inverse of standard error
pred_f2 <- funnel(ma_pred, yaxis = "seinv", 
      xlab = "Standarized residuals",
      ylab = "Precision (inverse of SE)",  col = c(alpha("orange", 0.5)))
```

### Egger's test

```{r}
#| label: fig-egger_pred
#| fig-cap: "Egger's test of publication bias"

pred_df_bias <- dt_pred %>% mutate(sqrt_inv_e_n = sqrt((Cn + Tn)/(Cn * Tn)))

pred_bias_model <- rma.mv(yi = lnRR,
                      V = lnRR_var, 
                      mods = ~ 1 + sqrt_inv_e_n,
                      random = list(~1 | Shared_control_ID,
                                ~1 | Cohort_ID,
                                ~1 | Obs_ID),
                      test = "t",
                      method = "REML", 
                      sparse = TRUE,
                      data = pred_df_bias)

summary(pred_bias_model)

bubble_plot(pred_bias_model,
            mod = "sqrt_inv_e_n",
            group = "Study_ID",
            xlab = "Square root of inverse of effective sample size")

```

### Decline effect
```{r}
#| label: fig-decline_pred
#| fig-cap: "Decline effect"

pred_year_model <- rma.mv(yi = lnRR,
                      V = VCV_pred, 
                      mods = ~  1 + Year,
                      random = list(~1 | Shared_control_ID,
                                ~1 | Cohort_ID,
                                ~1 | Obs_ID),
                      test = "t",
                      method = "REML", 
                      sparse = TRUE,
                      data = pred_df_bias)

summary(pred_year_model)

bubble_plot(pred_year_model,
            mod = "Year",
            group = "Study_ID",
            xlab = "Year of publication")

```

### multi-moderator model
```{r}

pred_bias_all <- rma.mv(yi = lnRR,
                      V = VCV_pred, 
                      mods = ~ Treatment_stimulus + Log_area + Number_pattern + Type_prey+ sqrt_inv_e_n + Year,
                      random = list(~1 | Shared_control_ID,
                                ~1 | Cohort_ID,
                                ~1 | Obs_ID),
                      test = "t",
                      method = "REML", 
                      sparse = TRUE,
                      data = pred_df_bias)

summary(pred_bias_all)
```


:::

## Additional analyses
### Background area (mm²)
```{r}
#| label: fig-background_pred
#| fig-cap: "Effect size and background area"

pred_mr_background <- rma.mv(yi = lnRR,
                        V = VCV_pred, 
                        mods = ~ Log_background,
                  random = list(~1 | Shared_control_ID,
                                ~1 | Cohort_ID,
                                ~1 | Obs_ID),
                        test = "t",
                        method = "REML",
                        sparse = TRUE,
                        data = dt_pred)

summary(pred_mr_background)

bubble_plot(pred_mr_background,
            mod = "Log_background",
            group = "Study_ID",
            xlab = "Log-transformed backgroud")

```


## Figure galary
:::{.panel-tabset}

### Discrete moderators
```{r}
#| label: fig-galary1_pred
#| fig-cap: "Discrete moderators"


# overall effect
pred_p1 <- orchard_plot(ma_pred,
                    group = "Study_ID",
                    xlab = "log response ratio (lnRR)", 
                    angle = 45,
                    legend.pos = "bottom.right") + 
                    scale_x_discrete(labels = c("Overall effect")) + 
                    theme(legend.direction = "horizontal",
                    legend.text = element_text(size = 6)) +
                    
                    scale_colour_okabe_ito()+
                    scale_fill_okabe_ito()

#eyespot vs. conspicuous patterns
pred_p2 <- orchard_plot(pred_mr_eyespot,
                  mod = "Treatment_stimulus",
                  group = "Study_ID",
                  xlab = "log response ratio (lnRR)",
                  angle = 45,
                  legend.pos = "bottom.right") +
                  theme(legend.direction = "horizontal",
                  legend.text = element_text(size = 6)) +
                  scale_colour_okabe_ito(order = 2:3)+
                  scale_fill_okabe_ito(order = 2:3)
                  
# prey type - real vs. artificial
pred_p3 <- orchard_plot(pred_mr_prey_type,
                  mod = "Type_prey",
                  group = "Study_ID",
                  xlab = "log response ratio (lnRR)",
                  angle = 45,
                  legend.pos = "bottom.right") +
                  theme(legend.direction = "horizontal",
                  legend.text = element_text(size = 6))+ 
                  scale_colour_okabe_ito(order = 4:5) +
                  scale_fill_okabe_ito(order = 4:5)

# combine
pred_patch1 <- pred_p1 | (pred_p2 / pred_p3)
pred_patch1 + plot_annotation(tag_levels = "a")

# output figure as pdf
# ggsave("fig1.pdf", width = 10, height = 5, dpi = 450)

```

### Continuous moderators
```{r}
#| label: fig-galary2_pred
#| fig-cap: "Continuous moderators"


# these figs were created by multi meta-regression model results
# log-transformed area
pred_p4 <- bubble_plot(pred_mr_area,
                  mod = "Log_area",
                  group = "Study_ID",
                  xlab = "Log-transformed area") +
                  scale_x_continuous(breaks = seq(0,7,1.5)) +
                  scale_y_continuous(breaks = seq(-2.5, 4.5, 1.5))

# number of patterns
pred_p5 <- bubble_plot(pred_mr_num,
            mod = "Number_pattern",
            group = "Study_ID",
            xlab = "Number of patterns") +
                  scale_x_continuous(breaks = seq(0,11,1.5)) +
                  scale_y_continuous(breaks = seq(-2.5, 4.5, 1.5))

# combine
pred_p4 / pred_p5 + plot_annotation(tag_levels = "a")

# output figure as pdf
# ggsave("fig2_multi.pdf", width = 10, height = 10, dpi = 450)
```

### Publication bias

```{r}
#| label: fig-galary3_pred
#| fig-cap: "Publication bias"
#| fig-subcap:
#|    - "Funnel plot"
#|    - "Egger's test and Decline effect"
#| layout-ncol: 2

# funnel plot

# pdf("fig3.pdf")

funnel(ma_pred, yaxis = "seinv", 
      xlab = "Standarised residuals",
      ylab = "Precision (inverse of SE)",
      xlim = c(-4.0, 4.5), 
      ylim = c(0.01, 80.0), 
      col = c(alpha("mediumvioletred", 0.5)),
      cex = 0.7)

# dev.off()

# Egger's test and decline effect
pred_p7 <- bubble_plot(pred_bias_model,
            mod = "sqrt_inv_e_n",
            group = "Study_ID",
            xlab = "Square root of inverse of effective sample size") +
            scale_y_continuous(breaks = seq(-2.5, 4.5, 1.5)) 

pred_p8 <- bubble_plot(pred_year_model,
            mod = "Year",
            group = "Study_ID",
            xlab = "Year of publication") +  scale_y_continuous(breaks = seq(-2.5, 4.0, 1.5)) 

# combine plots created by bubble_plot()
pred_pub <- pred_p7 / pred_p8
pred_pub +  plot_annotation(tag_levels = 'a') 

# output figure as pdf
# ggsave("fig4.pdf", width = 10, height = 10, dpi = 450)

```
:::

# Meta-analysis - prey dataset

We used meta-analytical models to calculate total I2 (a measure of heterogeneity not caused by sampling error; Higgins. et al., 2003) and the partial I2 explained by each random factor.


```{r}

ma_prey <- rma.mv(yi = lnRR,
                  V = VCV_prey, 
                  random = list(~1 | Study_ID,
                                ~1 | Shared_control_ID,
                                ~1 | Cohort_ID,
                                ~1 | Obs_ID),
                  test = "t",
                  method = "REML", 
                  sparse = TRUE,
                  data = dt_prey)

summary(ma_prey)

prey_i2 <- round(i2_ml(ma_prey), 4)

prey_r2 <- round(r2_ml(ma_prey), 4)
```

```{r}
#| echo: false
prey_t_i2 <- t(prey_i2)
prey_t_r2 <- t(prey_r2)
knitr::kable(prey_t_i2)
knitr::kable(prey_t_r2)
```
**Table 3 - Heterogeneity of effect size**

```{r}
#| label: fig-ma_prey
#| fig-cap: "Estimates of overprey effect size and 95% confidence intervals"
#| fig-cap-location: bottom

orchard_plot(ma_prey,
              group = "Study_ID",
              xlab = "log response ratio (lnRR)", 
              angle = 45) + 
              scale_x_discrete(labels = c("Overall effect")) + 
              scale_colour_okabe_ito()+
              scale_fill_okabe_ito()

```

## Meta-regressions: uni-moderator - preyetor dataset

:::{.panel-tabset}

### Pattern type
Eyespot vs. conspicuous patterns - Is there significant difference of effect size between two patterns?

```{r}

#normal model
prey_mr_eyespot <- rma.mv(yi = lnRR,
                    V = VCV_prey, 
                    mods = ~ Treatment_stimulus,
                  random = list(~1 | Study_ID,
                                ~1 | Shared_control_ID,
                                ~1 | Cohort_ID,
                                ~1 | Obs_ID),
                    test = "t",
                    method = "REML", 
                    sparse = TRUE,
                    data = dt_prey)

summary(prey_mr_eyespot)

prey_r2_1 <- round(r2_ml(prey_mr_eyespot), 4)
```

```{r}
#| echo: false


prey_t_r2_1 <- t(prey_r2_1)
knitr::kable(prey_t_r2_1)  
```
**Table XX. Model goodness-of-fit**


```{r}
#| label: fig-eyespot_prey
#| fig-cap: "Eyespot vs. conspicuous patterns"

orchard_plot(prey_mr_eyespot,
            mod = "Treatment_stimulus",
            group = "Study_ID",
            xlab = "log response ratio (lnRR)",
            angle = 45) + 
            scale_colour_okabe_ito(order = 2:3)+
            scale_fill_okabe_ito(order = 2:3)

```


```{r}

# intercept-removed model
prey_mr_eyespot1 <- rma.mv(yi = lnRR,
                      V = VCV_prey, 
                      mods = ~ Treatment_stimulus -1,
                  random = list(~1 | Study_ID,
                                ~1 | Shared_control_ID,
                                ~1 | Cohort_ID,
                                ~1 | Obs_ID),
                      test = "t",
                      method = "REML", 
                      sparse = TRUE,
                      data = dt_prey)

summary(prey_mr_eyespot1)

```

### Pattern diameter (mm) 

```{r}
#| label: fig-diameter_prey
#| fig-cap: "Effect size and pattern diameter"

prey_mr_diameter <- rma.mv(yi = lnRR,
                      V = VCV_prey, 
                      mods = ~ Log_diameter,
                  random = list(~1 | Study_ID,
                                ~1 | Shared_control_ID,
                                ~1 | Cohort_ID,
                                ~1 | Obs_ID),
                      test = "t",
                      method = "REML", 
                      sparse = TRUE,
                      data = dt_prey)

summary(prey_mr_diameter)


prey_r2_2 <- round(r2_ml(prey_mr_diameter), 4)
```

```{r}
#| echo: false


prey_t_r2_2 <- t(prey_r2_2)
knitr::kable(prey_t_r2_2)  
```
**Table XX. Model goodness-of-fit**

```{r}

bubble_plot(prey_mr_diameter,
            mod = "Log_diameter",
            group = "Study_ID",
            xlab = "Log-transformed diameter")

```

### Pattern area (mm²)

```{r}
#| label: fig-area_prey
#| fig-cap: "Effect size and pattern area"

prey_mr_area <- rma.mv(yi = lnRR,
                  V = VCV_prey, 
                  mods = ~ Log_area,
                  random = list(~1 | Study_ID,
                                ~1 | Shared_control_ID,
                                ~1 | Cohort_ID,
                                ~1 | Obs_ID),
                  test = "t",
                  method = "REML", 
                  sparse = TRUE,
                  data = dt_prey)

summary(prey_mr_area)

prey_r2_3 <- round(r2_ml(prey_mr_area), 4)
```

```{r}
#| echo: false

prey_t_r2_3 <- t(prey_r2_3)
knitr::kable(prey_t_r2_3)  
```
**Table XX. Model goodness-of-fit**

```{r}

bubble_plot(prey_mr_area,
            mod = "Log_area",
            group = "Study_ID",
            xlab = "Log-transformed area")

```

### Pattern number

```{r}
#| label: fig-number_prey
#| fig-cap: "Effect size and number of patterns"

prey_mr_num <- rma.mv(yi = lnRR,
                  V = VCV_prey,
                  mods = ~ Number_pattern,
                  random = list(~1 | Study_ID,
                                ~1 | Shared_control_ID,
                                ~1 | Cohort_ID,
                                ~1 | Obs_ID),
                      test = "t",
                      method = "REML",
                      sparse = TRUE,
                      data = dt_prey)

summary(prey_mr_num)

prey_r2_4 <- round(r2_ml(prey_mr_num), 4)
```

```{r}
#| echo: false

prey_t_r2_4 <- t(prey_r2_4)
knitr::kable(prey_t_r2_4)  
```

**Table XX. Model goodness-of-fit**
  
```{r}

bubble_plot(prey_mr_num,
            mod = "Number_pattern",
            group = "Study_ID",
            xlab = "Number of patterns") 

```


### Prey material type
Our dataset includes two material types of prey: live and artificial. Is there significant difference of effect size between two stimuli?
```{r}
#| label: fig-stimuli_prey
#| fig-cap: "Effect size and prey type - real vs. artificial"

# normal model
prey_mr_prey_type <- rma.mv(yi = lnRR,
                  V = VCV_prey, 
                  mods = ~ Type_prey,
                  random = list(~1 | Study_ID,
                                ~1 | Shared_control_ID,
                                ~1 | Cohort_ID,
                                ~1 | Obs_ID),
                  test = "t",
                  method = "REML", 
                  sparse = TRUE,
                  data = dt_prey)

summary(prey_mr_prey_type)

prey_r2_5 <- round(r2_ml(prey_mr_prey_type), 4)

```

```{r}
#| echo: false

prey_t_r2_5 <- t(prey_r2_5)
knitr::kable(prey_t_r2_5)

```
**Table XX. Model goodness-of-fit**

```{r}

orchard_plot(prey_mr_prey_type,
              mod = "Type_prey",
              group = "Study_ID",
              xlab = "Type of prey",
              angle = 45) +
            scale_colour_okabe_ito(order = 4:5)+
            scale_fill_okabe_ito(order = 4:5)


# intercept-removed model
prey_mr_prey_type1 <- rma.mv(yi = lnRR,
                            V = VCV_prey, 
                            mods = ~ Type_prey -1,
                            random = list(~1 | Study_ID,
                                ~1 | Shared_control_ID,
                                ~1 | Cohort_ID,
                                ~1 | Obs_ID),
                            test = "t",
                            method = "REML", 
                            sparse = TRUE,
                            data = dt_prey)

summary(prey_mr_prey_type1)
```

### Prey shape type
Our dataset includes 4 types of prey type: real butterfly, abstract butterfly, abstract caterpillar, and abstract prey. Is there significant difference of effect size between two stimuli?

```{r}

prey_mr_prey_shape <- rma.mv(yi = lnRR,
                        V = VCV_prey, 
                        mods = ~ Shape_prey -1,
                        random = list(~1 | Study_ID,
                                ~1 | Shared_control_ID,
                                ~1 | Cohort_ID,
                                ~1 | Obs_ID),
                        test = "t",
                        method = "REML", 
                        sparse = TRUE,
                        data = dt_prey)

summary(prey_mr_prey_shape)

prey_r2_6 <- round(r2_ml(prey_mr_prey_shape), 4)
```

```{r}
#| echo: false

prey_t_r2_6 <- t(prey_r2_6)
knitr::kable(prey_t_r2_6)  
```
**Table XX. Model goodness-of-fit**

```{r}
#| label: fig-shape_prey
#| fig-cap: "Effect size and prey shape"

orchard_plot(prey_mr_prey_shape,
              mod = "Shape_prey",
              group = "Study_ID",
              xlab = "Shape of prey",
              angle = 45) +
              scale_colour_okabe_ito(order = 6:9)+
              scale_fill_okabe_ito(order = 6:9)

```

:::

## Correlation visualisation and choose moderators for multi-moderator meta-regression in preyator dataset
Before we run multi-moderator meta-regressions, we need to consider the correlation between moderators.
Area, diameter and background seem to be correlated. We visualised the correlation between these variables.

:::{.panel-tabset}

### Visualisation of correlation

```{r}
#| label: fig-cor-continuous_prey
#| fig-cap: "Correlation between coninuous moderators"

# correlation between continuous variables
prey_corr_cont <- round(cor(dt_prey[, c("Diameter_pattern", "Area_pattern", "Number_pattern", "Area_background")]),2)

prey_p1 <- ggcorrplot(prey_corr_cont, hc.order = TRUE, lab = TRUE, outline.col = "white", colors = c("#6D9EC1", "white", "#E46726"), title = "(a) Continuous variables")

prey_corr_cont_log <- round(cor(dt_prey[, c("Log_diameter", "Log_area", "Number_pattern", "Log_background")]),2)

prey_p2 <- ggcorrplot(prey_corr_cont_log, hc.order = TRUE, lab = TRUE, outline.col = "white", colors = c("#6D9EC1", "white", "#E46726"), title = "(b) Log-transormed continuous variables")

prey_p1 + prey_p2 +plot_layout(guides = 'collect')
```

```{r}
#| label: fig-cor-categorical_prey
#| fig-cap: "Correlation between categorical variables"

prey_dat1 <- dt_prey %>%
  dplyr::select("Treatment_stimulus", "Type_prey", "Shape_prey")

prey_corr_cat <- GKtauDataframe(prey_dat1)
plot(prey_corr_cat)

```
We should not include "Shape_prey" and "Type_prey" in the model at the same time. Because they are correlated.

### Choose moderators
We used model R2 values to find better model and modelator VIF values to check multicollinearity between moderators. 
Higher R2 indicates better model and VIF > 2 indicates multicollinearity. 

#### R2
```{r}

prey_r2_area <- rma.mv(yi = lnRR,
                  V = VCV_prey,
                  mods = ~ Log_area + Number_pattern,
                  random = list(~1 | Study_ID,
                                ~1 | Shared_control_ID,
                                ~1 | Cohort_ID,
                                ~1 | Obs_ID),
                  test = "t",
                  method = "REML",
                  sparse = TRUE,
                  data = dt_prey)

prey_r2_diameter <- rma.mv(yi = lnRR,
                      V = VCV_prey,
                      mods = ~ Log_diameter + Number_pattern,
                  random = list(~1 | Study_ID,
                                ~1 | Shared_control_ID,
                                ~1 | Cohort_ID,
                                ~1 | Obs_ID),
                      test = "t",
                      method = "REML",
                      sparse = TRUE,
                      data = dt_prey)

# check r2 values
r2_ml(prey_r2_area)
r2_ml(prey_r2_diameter)

```
It seems **area** is a better preyictor than **diameter** .

:::

## Meta-regressions: multi-moderator

:::{.panel-tabset}

### All potential moderators (full model)
Include all moderators in the model.

```{r}

prey_mr_all <- rma.mv(yi = lnRR,
                V = VCV_prey, 
                mods = ~ Treatment_stimulus + Log_area 
                + Number_pattern + Type_prey,
                  random = list(~1 | Study_ID,
                                ~1 | Shared_control_ID,
                                ~1 | Cohort_ID,
                                ~1 | Obs_ID),
                test = "t",
                method = "REML", 
                sparse = TRUE,
                data = dt_prey)

summary(prey_mr_all)

r2_ml(prey_mr_all)
```

### Moderators associated with conspicuousness
Only include moderators related to conspicuousness (pattern area and number of patterns) in the model.

```{r}

prey_mr_cons <- rma.mv(yi = lnRR,
                V = VCV_prey, 
                mods = ~ Log_area + Number_pattern,
                random = list(~1 | Study_ID,
                                ~1 | Shared_control_ID,
                                ~1 | Cohort_ID,
                                ~1 | Obs_ID),
                test = "t",
                method = "REML", 
                sparse = TRUE,
                data = dt_prey)

summary(prey_mr_cons)

r2_ml(prey_mr_cons)

bubble_plot(prey_mr_cons,
            mod = "Log_area",
            group = "Study_ID",
            xlab = "Log-transformed area")

```


```{r}
prey_mr_cons_1 <- rma.mv(yi = lnRR,
                V = VCV_prey, 
                mods = ~ Log_area + Number_pattern + Treatment_stimulus,
                  random = list(~1 | Study_ID,
                                ~1 | Shared_control_ID,
                                ~1 | Cohort_ID,
                                ~1 | Obs_ID),
                test = "t",
                method = "REML", 
                sparse = TRUE,
                data = dt_prey)

summary(prey_mr_cons_1)

r2_ml(prey_mr_cons_1)

```

### Moderators associated with prey in preyator dataset
```{r}
prey_mr_pre <- rma.mv(yi = lnRR,
                V = VCV_prey, 
                mods = ~ Treatment_stimulus + Type_prey,
                random = list(~1 | Study_ID,
                                ~1 | Shared_control_ID,
                                ~1 | Cohort_ID,
                                ~1 | Obs_ID),
                test = "t",
                method = "REML", 
                sparse = TRUE,
                data = dt_prey)

summary(prey_mr_pre)

r2_ml(prey_mr_pre)
```
:::

## Publication bias

:::{.panel-tabset}

### Funnel plot

```{r}
#| layout-ncol: 2
#| label: fig-funnel_prey
#| fig-cap: "Funnel plot of effect size and its standard error"
#| fig-subcap: 
#|   - "Effect size and its standard error"
#|   - "Effect size and its inverse standard error"

# funnel plot - standard error
funnel(ma_prey, yaxis = "sei", 
      xlab = "Standarised residuals",
      ylab = "Precision (inverse of SE)" )

# funnel plot - inverse of standard error
prey_f2 <- funnel(ma_prey, yaxis = "seinv", 
      xlab = "Standarized residuals",
      ylab = "Precision (inverse of SE)",  col = c(alpha("orange", 0.5)))
```

### Egger's test

```{r}
#| label: fig-egger_prey
#| fig-cap: "Egger's test of publication bias"

prey_df_bias <- dt_prey %>% mutate(sqrt_inv_e_n = sqrt((Cn + Tn)/(Cn * Tn)))

prey_bias_model <- rma.mv(yi = lnRR,
                      V = lnRR_var, 
                      mods = ~ 1 + sqrt_inv_e_n,
                      random = list(~1 | Study_ID,
                                ~1 | Shared_control_ID,
                                ~1 | Cohort_ID,
                                ~1 | Obs_ID),
                      test = "t",
                      method = "REML", 
                      sparse = TRUE,
                      data = prey_df_bias)

summary(prey_bias_model)

bubble_plot(prey_bias_model,
            mod = "sqrt_inv_e_n",
            group = "Study_ID",
            xlab = "Square root of inverse of effective sample size")

```

### Decline effect
```{r}
#| label: fig-decline_prey
#| fig-cap: "Decline effect"

prey_year_model <- rma.mv(yi = lnRR,
                      V = VCV_prey, 
                      mods = ~  1 + Year,
                      random = list(~1 | Study_ID,
                                ~1 | Shared_control_ID,
                                ~1 | Cohort_ID,
                                ~1 | Obs_ID),
                      test = "t",
                      method = "REML", 
                      sparse = TRUE,
                      data = prey_df_bias)

summary(prey_year_model)

bubble_plot(prey_year_model,
            mod = "Year",
            group = "Study_ID",
            xlab = "Year of publication")

```

### multi-moderator model
```{r}

prey_bias_all <- rma.mv(yi = lnRR,
                      V = VCV_prey, 
                      mods = ~ Treatment_stimulus + Log_area + Number_pattern + Type_prey+ sqrt_inv_e_n + Year,
                      random = list(~1 | Study_ID,
                                ~1 | Shared_control_ID,
                                ~1 | Cohort_ID,
                                ~1 | Obs_ID),
                      test = "t",
                      method = "REML", 
                      sparse = TRUE,
                      data = prey_df_bias)

summary(prey_bias_all)
```


:::

## Additional analyses

### Background area (mm²)
```{r}
#| label: fig-background_prey
#| fig-cap: "Effect size and background area"

prey_mr_background <- rma.mv(yi = lnRR,
                        V = VCV_prey, 
                        mods = ~ Log_background,
                        random = list(~1 | Study_ID,
                                ~1 | Shared_control_ID,
                                ~1 | Cohort_ID,
                                ~1 | Obs_ID),
                        test = "t",
                        method = "REML",
                        sparse = TRUE,
                        data = dt_prey)

summary(prey_mr_background)

bubble_plot(prey_mr_background,
            mod = "Log_background",
            group = "Study_ID",
            xlab = "Log-transformed backgroud")

```


## Figure galary
:::{.panel-tabset}

### Discrete moderators
```{r}
#| label: fig-galary1_prey
#| fig-cap: "Discrete moderators"


# overall effect
prey_p1 <- orchard_plot(ma_prey,
                    group = "Study_ID",
                    xlab = "log response ratio (lnRR)", 
                    angle = 45,
                    legend.pos = "bottom.right") + 
                    scale_x_discrete(labels = c("Overall effect")) + 
                    theme(legend.direction = "horizontal",
                    legend.text = element_text(size = 6)) +
                    
                    scale_colour_okabe_ito()+
                    scale_fill_okabe_ito()

#eyespot vs. conspicuous patterns
prey_p2 <- orchard_plot(prey_mr_eyespot,
                  mod = "Treatment_stimulus",
                  group = "Study_ID",
                  xlab = "log response ratio (lnRR)",
                  angle = 45,
                  legend.pos = "bottom.right") +
                  theme(legend.direction = "horizontal",
                  legend.text = element_text(size = 6)) +
                  scale_colour_okabe_ito(order = 2:3)+
                  scale_fill_okabe_ito(order = 2:3)
                  
# prey type - real vs. artificial
prey_p3 <- orchard_plot(prey_mr_prey_type,
                  mod = "Type_prey",
                  group = "Study_ID",
                  xlab = "log response ratio (lnRR)",
                  angle = 45,
                  legend.pos = "bottom.right") +
                  theme(legend.direction = "horizontal",
                  legend.text = element_text(size = 6))+ 
                  scale_colour_okabe_ito(order = 4:5) +
                  scale_fill_okabe_ito(order = 4:5)

# combine
prey_patch1 <- prey_p1 | (prey_p2 / prey_p3)
prey_patch1 + plot_annotation(tag_levels = "a")

# output figure as pdf
# ggsave("fig1.pdf", width = 10, height = 5, dpi = 450)

```

### Continuous moderators
```{r}
#| label: fig-galary2_prey
#| fig-cap: "Continuous moderators"


# these figs were created by multi meta-regression model results
# log-transformed area
prey_p4 <- bubble_plot(prey_mr_area,
                  mod = "Log_area",
                  group = "Study_ID",
                  xlab = "Log-transformed area") +
                  scale_x_continuous(breaks = seq(0,7,1.5)) +
                  scale_y_continuous(breaks = seq(-2.5, 4.5, 1.5))

# number of patterns
prey_p5 <- bubble_plot(prey_mr_num,
            mod = "Number_pattern",
            group = "Study_ID",
            xlab = "Number of patterns") +
                  scale_x_continuous(breaks = seq(0,11,1.5)) +
                  scale_y_continuous(breaks = seq(-2.5, 4.5, 1.5))

# combine
prey_p4 / prey_p5 + plot_annotation(tag_levels = "a")

# output figure as pdf
# ggsave("fig2_multi.pdf", width = 10, height = 10, dpi = 450)
```

### Publication bias

```{r}
#| label: fig-galary3_prey
#| fig-cap: "Publication bias"
#| fig-subcap:
#|    - "Funnel plot"
#|    - "Egger's test and Decline effect"
#| layout-ncol: 2

# funnel plot

# pdf("fig3.pdf")

funnel(ma_prey, yaxis = "seinv", 
      xlab = "Standarised residuals",
      ylab = "Precision (inverse of SE)",
      xlim = c(-4.0, 4.5), 
      ylim = c(0.01, 80.0), 
      col = c(alpha("mediumvioletred", 0.5)),
      cex = 0.7)

# dev.off()

# Egger's test and decline effect
prey_p7 <- bubble_plot(prey_bias_model,
            mod = "sqrt_inv_e_n",
            group = "Study_ID",
            xlab = "Square root of inverse of effective sample size") +
            scale_y_continuous(breaks = seq(-2.5, 4.5, 1.5)) 

prey_p8 <- bubble_plot(prey_year_model,
            mod = "Year",
            group = "Study_ID",
            xlab = "Year of publication") +  scale_y_continuous(breaks = seq(-2.5, 4.0, 1.5)) 

# combine plots created by bubble_plot()
prey_pub <- prey_p7 / prey_p8
prey_pub +  plot_annotation(tag_levels = 'a') 

# output figure as pdf
# ggsave("fig4.pdf", width = 10, height = 10, dpi = 450)

```


# Meta-analysis - all dataset

We used meta-analytical models to calculate total I2 (a measure of heterogeneity not caused by sampling error; Higgins. et al., 2003) and the partial I2 explained by each random factor.

::: callout-note
## Which random effects remove in our models?

We can remove _Shared control ID_ and _Cohort ID_
:::

```{r}
# I exclude cohort_ID because sigma^2.2 = 0 and I2 = 0
ma_all <- rma.mv(yi = lnRR,
                  V = VCV, 
                  random = list(~1 | Study_ID,
                                ~1 | Shared_control_ID,
                                ~1 | Cohort_ID,
                                ~1 | Obs_ID),
                  test = "t",
                  method = "REML", 
                  sparse = TRUE,
                  data = dt_all)

summary(ma_all)
i2 <- round(i2_ml(ma_all), 4)
r2 <- round(r2_ml(ma_all), 4)
```

```{r}
#| echo: false
t_i2 <- t(i2)
t_r2 <- t(r2)
knitr::kable(t_i2)
knitr::kable(t_r2)
```
**Table 3 - Heterogeneity of effect size**

```{r}
#| label: fig-ma_all
#| fig-cap: "Estimates of overall effect size and 95% confidence intervals"
#| fig-cap-location: bottom

orchard_plot(ma_all,
              group = "Study_ID",
              xlab = "log response ratio (lnRR)", 
              angle = 45) + 
              scale_x_discrete(labels = c("Overall effect")) + 
              scale_colour_okabe_ito()+
              scale_fill_okabe_ito()

```

## Meta-regressions: uni-moderator

:::{.panel-tabset}

### Pattern type
Eyespot vs. conspicuous patterns - Is there significant difference of effect size between two patterns?

```{r}

#normal model
mr_eyespot <- rma.mv(yi = lnRR,
                    V = VCV, 
                    mods = ~ Treatment_stimulus,
                    random = list(~1 | Study_ID,
                                  ~1 | Obs_ID),
                    test = "t",
                    method = "REML", 
                    sparse = TRUE,
                    data = dt_all)

summary(mr_eyespot)

r2_1 <- round(r2_ml(mr_eyespot), 4)
```

```{r}
#| echo: false


t_r2_1 <- t(r2_1)
knitr::kable(t_r2_1)  
```
**Table XX. Model goodness-of-fit**


```{r}
#| label: fig-eyespot
#| fig-cap: "Eyespot vs. conspicuous patterns"

orchard_plot(mr_eyespot,
            mod = "Treatment_stimulus",
            group = "Study_ID",
            xlab = "log response ratio (lnRR)",
            angle = 45) + 
            scale_colour_okabe_ito(order = 2:3)+
            scale_fill_okabe_ito(order = 2:3)

```


```{r}

# intercept-removed model
mr_eyespot1 <- rma.mv(yi = lnRR,
                      V = VCV, 
                      mods = ~ Treatment_stimulus -1,
                      random = list(~1 | Study_ID,
                                    ~1 | Obs_ID),
                      test = "t",
                      method = "REML", 
                      sparse = TRUE,
                      data = dt_all)

summary(mr_eyespot1)

```

### Pattern diameter (mm) 

```{r}
#| label: fig-diameter
#| fig-cap: "Effect size and pattern diameter"

mr_diameter <- rma.mv(yi = lnRR,
                      V = VCV, 
                      mods = ~ Log_diameter,
                      random = list(~1 | Study_ID,
                                    ~1 | Obs_ID),
                      test = "t",
                      method = "REML", 
                      sparse = TRUE,
                      data = dt_all)

summary(mr_diameter)


r2_2 <- round(r2_ml(mr_diameter), 4)
```

```{r}
#| echo: false


t_r2_2 <- t(r2_2)
knitr::kable(t_r2_2)  
```
**Table XX. Model goodness-of-fit**

```{r}

bubble_plot(mr_diameter,
            mod = "Log_diameter",
            group = "Study_ID",
            xlab = "Log-transformed diameter")

```

### Pattern area (mm²)

```{r}
#| label: fig-area
#| fig-cap: "Effect size and pattern area"

mr_area <- rma.mv(yi = lnRR,
                  V = VCV, 
                  mods = ~ Log_area,
                  random = list(~1 | Study_ID,
                                ~1 | Obs_ID),
                  test = "t",
                  method = "REML", 
                  sparse = TRUE,
                  data = dt_all)

summary(mr_area)

r2_3 <- round(r2_ml(mr_area), 4)
```

```{r}
#| echo: false

t_r2_3 <- t(r2_3)
knitr::kable(t_r2_3)  
```
**Table XX. Model goodness-of-fit**

```{r}

bubble_plot(mr_area,
            mod = "Log_area",
            group = "Study_ID",
            xlab = "Log-transformed area")

```

### Pattern number

```{r}
#| label: fig-number
#| fig-cap: "Effect size and number of patterns"

mr_num <- rma.mv(yi = lnRR,
                  V = VCV,
                  mods = ~ Number_pattern,
                  random = list(~1 | Study_ID,
                                ~1 | Obs_ID),
                      test = "t",
                      method = "REML",
                      sparse = TRUE,
                      data = dt_all)

summary(mr_num)

r2_4 <- round(r2_ml(mr_num), 4)
```

```{r}
#| echo: false

t_r2_4 <- t(r2_4)
knitr::kable(t_r2_4)  
```

**Table XX. Model goodness-of-fit**
  
```{r}

bubble_plot(mr_num,
            mod = "Number_pattern",
            group = "Study_ID",
            xlab = "Number of patterns") 

```

### Background area (mm²)
```{r}
#| label: fig-background
#| fig-cap: "Effect size and background area"

mr_background <- rma.mv(yi = lnRR,
                        V = VCV, 
                        mods = ~ Log_background,
                        random = list(~1 | Study_ID,
                                      ~1 | Obs_ID),
                        test = "t",
                        method = "REML",
                        sparse = TRUE,
                        data = dt_all)

summary(mr_background)

r2_ml(mr_background)


bubble_plot(mr_background,
            mod = "Log_background",
            group = "Study_ID",
            xlab = "Log-transformed backgroud")

```

### Prey material type
Our dataset includes two material types of prey: live and artificial. Is there significant difference of effect size between two stimuli?
```{r}
#| label: fig-stimuli
#| fig-cap: "Effect size and prey type - real vs. artificial"

# normal model
mr_prey_type <- rma.mv(yi = lnRR,
                  V = VCV, 
                  mods = ~ Type_prey,
                  random = list(~1 | Study_ID,
                                ~1 | Obs_ID),
                  test = "t",
                  method = "REML", 
                  sparse = TRUE,
                  data = dt_all)

summary(mr_prey_type)

r2_5 <- round(r2_ml(mr_prey_type), 4)

```

```{r}
#| echo: false

t_r2_5 <- t(r2_5)
knitr::kable(t_r2_5)

```
**Table XX. Model goodness-of-fit**

```{r}

orchard_plot(mr_prey_type,
              mod = "Type_prey",
              group = "Study_ID",
              xlab = "Type of prey",
              angle = 45) +
            scale_colour_okabe_ito(order = 4:5)+
            scale_fill_okabe_ito(order = 4:5)


# intercept-removed model
mr_prey_type1 <- rma.mv(yi = lnRR,
                        V = VCV, 
                        mods = ~ Type_prey -1,
                        random = list(~1 | Study_ID,
                                      ~1 | Obs_ID),
                        test = "t",
                        method = "REML", 
                        sparse = TRUE,
                        data = dt_all)

summary(mr_prey_type1)
```

### Prey shape type
Our dataset includes 4 types of prey type: real butterfly, abstract butterfly, abstract caterpillar, and abstract prey. Is there significant difference of effect size between two stimuli?

```{r}

mr_prey_shape <- rma.mv(yi = lnRR,
                        V = VCV, 
                        mods = ~ Shape_prey -1,
                        random = list(~1 | Study_ID,
                                      ~1 | Obs_ID),
                                      test = "t",
                                      method = "REML", 
                                      sparse = TRUE,
                                      data = dt_all)

summary(mr_prey_shape)

r2_6 <- round(r2_ml(mr_prey_shape), 4)

dat_all$Shape_prey <- factor(dat_all$Shape_prey)
levels(dat_all$Shape_prey)

mat_ex <- 
    cbind(contrMat(rep(1,
                       length(mr_prey_shape$ci.ub)),
                   type = "Tukey"))
sig_test <- summary(glht(mr_prey_shape, linfct= mat_ex), test = adjusted("none"))

sig_test
```

```{r}
#| echo: false

t_r2_6 <- t(r2_6)
knitr::kable(t_r2_6)  
```
**Table XX. Model goodness-of-fit**

```{r}
#| label: fig-shape
#| fig-cap: "Effect size and prey shape"

orchard_plot(mr_prey_shape,
              mod = "Shape_prey",
              group = "Study_ID",
              xlab = "Shape of prey",
              angle = 45) +
              scale_colour_okabe_ito(order = 6:9)+
              scale_fill_okabe_ito(order = 6:9)

```

:::

## Correlation visualisation and choose moderators
Before we run multi-moderator meta-regressions, we need to consider the correlation between moderators.
Area, diameter and background seem to be correlated. We visualised the correlation between these variables.

:::{.panel-tabset}

### Visualisation of correlation

```{r}
#| label: fig-cor-continuous
#| fig-cap: "Correlation between coninuous moderators"

# correlation between continuous variables
corr_cont <- round(cor(dt_all[, c("Diameter_pattern", "Area_pattern", "Number_pattern", "Area_background")]),2)

p1 <- ggcorrplot(corr_cont, hc.order = TRUE, lab = TRUE, outline.col = "white", colors = c("#6D9EC1", "white", "#E46726"), title = "(a) Continuous variables")

corr_cont_log <- round(cor(dt_all[, c("Log_diameter", "Log_area", "Number_pattern", "Log_background")]),2)

p2 <- ggcorrplot(corr_cont_log, hc.order = TRUE, lab = TRUE, outline.col = "white", colors = c("#6D9EC1", "white", "#E46726"), title = "(b) Log-transormed continuous variables")

p1 + p2 +plot_layout(guides = 'collect')
```

```{r}
#| label: fig-cor-categorical
#| fig-cap: "Correlation between categorical variables"

dat1 <- dt_all %>%
  dplyr::select("Treatment_stimulus", "Type_prey", "Shape_prey")

corr_cat <- GKtauDataframe(dat1)
plot(corr_cat)

```
We should not include "Shape_prey" and "Type_prey" in the model at the same time. Because they are correlated.

### Choose moderators
We used model R2 values to find better model and modelator VIF values to check multicollinearity between moderators. 
Higher R2 indicates better model and VIF > 2 indicates multicollinearity. 

#### R2
```{r}

r2_area <- rma.mv(yi = lnRR,
                  V = VCV,
                  mods = ~ Log_area + Number_pattern,
                  random = list(~1 | Study_ID,
                                ~1 | Obs_ID),
                  test = "t",
                  method = "REML",
                  sparse = TRUE,
                  data = dt_all)

r2_diameter <- rma.mv(yi = lnRR,
                      V = VCV,
                      mods = ~ Log_diameter + Number_pattern,
                      random = list(~1 | Study_ID,
                                    ~1 | Obs_ID),
                      test = "t",
                      method = "REML",
                      sparse = TRUE,
                      data = dt_all)

# check r2 values
r2_ml(r2_area)
r2_ml(r2_diameter)

```
It seems **area** is a better predictor than **diameter** .

:::

## Meta-regressions: multi-moderator

:::{.panel-tabset}

### All potential moderators (full model)
Include all moderators in the model.

```{r}

mr_all <- rma.mv(yi = lnRR,
                V = VCV, 
                mods = ~ Treatment_stimulus + Log_area 
                + Number_pattern + Type_prey,
                random = list(~1 | Study_ID,
                              ~1 | Obs_ID),
                test = "t",
                method = "REML", 
                sparse = TRUE,
                data = dt_all)

summary(mr_all)

r2_ml(mr_all)
```

### Moderators associated with conspicuousness
Only include moderators related to conspicuousness (pattern area and number of patterns) in the model.

```{r}

mr_cons <- rma.mv(yi = lnRR,
                V = VCV, 
                mods = ~ Log_area + Number_pattern,
                random = list(~1 | Study_ID,
                              ~1 | Obs_ID),
                test = "t",
                method = "REML", 
                sparse = TRUE,
                data = dt_all)

summary(mr_cons)

r2_ml(mr_cons)

bubble_plot(mr_cons,
            mod = "Log_area",
            group = "Study_ID",
            xlab = "Log-transformed area")

```


```{r}
mr_cons_1 <- rma.mv(yi = lnRR,
                V = VCV, 
                mods = ~ Log_area + Number_pattern + Treatment_stimulus,
                random = list(~1 | Study_ID,
                              ~1 | Obs_ID),
                test = "t",
                method = "REML", 
                sparse = TRUE,
                data = dt_all)

summary(mr_cons_1)

r2_ml(mr_cons_1)

```

### Moderators associated with prey
```{r}
mr_pre <- rma.mv(yi = lnRR,
                V = VCV, 
                mods = ~ Treatment_stimulus + Type_prey,
                random = list(~1 | Study_ID,
                              ~1 | Obs_ID),
                test = "t",
                method = "REML", 
                sparse = TRUE,
                data = dt_all)

summary(mr_pre)

r2_ml(mr_pre)
```
:::

## Publication bias

:::{.panel-tabset}

### Funnel plot

```{r}
#| layout-ncol: 2
#| label: fig-funnel
#| fig-cap: "Funnel plot of effect size and its standard error"
#| fig-subcap: 
#|   - "Effect size and its standard error"
#|   - "Effect size and its inverse standard error"

# funnel plot - standard error
funnel(ma_all, yaxis = "sei", 
      xlab = "Standarised residuals",
      ylab = "Precision (inverse of SE)" )

# funnel plot - inverse of standard error
f2 <- funnel(ma_all, yaxis = "seinv", 
      xlab = "Standarized residuals",
      ylab = "Precision (inverse of SE)",  col = c(alpha("orange", 0.5)))
```

### Egger's test

```{r}
#| label: fig-egger
#| fig-cap: "Egger's test of publication bias"

df_bias <- dt_all %>% mutate(sqrt_inv_e_n = sqrt((Cn + Tn)/(Cn * Tn)))

bias_model <- rma.mv(yi = lnRR,
                      V = lnRR_var, 
                      mods = ~ 1 + sqrt_inv_e_n,
                      random = list(~1 | Study_ID,
                                    ~1 | Obs_ID),
                      test = "t",
                      method = "REML", 
                      sparse = TRUE,
                      data = df_bias)

summary(bias_model)

bubble_plot(bias_model,
            mod = "sqrt_inv_e_n",
            group = "Study_ID",
            xlab = "Square root of inverse of effective sample size")

```

### Decline effect
```{r}
#| label: fig-decline
#| fig-cap: "Decline effect"

year_model <- rma.mv(yi = lnRR,
                      V = VCV, 
                      mods = ~  1 + Year,
                      random = list(~1 | Study_ID,
                                    ~1 | Obs_ID),
                      test = "t",
                      method = "REML", 
                      sparse = TRUE,
                      data = df_bias)

summary(year_model)

bubble_plot(year_model,
            mod = "Year",
            group = "Study_ID",
            xlab = "Year of publication")

```

### Multi-moderator
```{r}

multi_bias <- rma.mv(yi = lnRR,
                      V = VCV, 
                      mods = ~ Treatment_stimulus + Log_area 
                             + Number_pattern + Type_prey
                             + sqrt_inv_e_n + Year,
                      random = list(~1 | Study_ID,
                                    ~1 | Obs_ID),
                      test = "t",
                      method = "REML", 
                      sparse = TRUE,
                      data = df_bias)

summary(multi_bias)

bubble_plot(multi_bias,
            mod = "sqrt_inv_e_n",
            group = "Study_ID",
            xlab = "Square root of inverse of effective sample size")

bubble_plot(multi_bias,
            mod = "Year",
            group = "Study_ID",
            xlab = "Year of publication")

```

:::

## Additional analyses

### Dataset
We compared effect size between two datasets (predator and prey) to see whether there is any difference in effect size between two datasets.

```{r}
#| label: fig-dataset
#| fig-cap: "Effect size and dataset - predator and prey"

mr_dataset <- rma.mv(yi = lnRR,
                      V = VCV,
                      mods = ~ Dataset,
                      random = list(~1 | Study_ID,
                                    ~1 | Obs_ID),
                      test = "t",
                      method = "REML",
                      sparse = TRUE,
                      data = dt_all)

summary(mr_dataset)

orchard_plot(mr_dataset,
            mod = "Dataset",
            group = "Study_ID",
            xlab = "Dataset", 
            angle = 45) 

```




## Figure galary
:::{.panel-tabset}

### Discrete moderators
```{r}
#| label: fig-galary1
#| fig-cap: "Discrete moderators"

# overall effect
p1 <- orchard_plot(ma_all,
                    group = "Study_ID",
                    xlab = "log response ratio (lnRR)", 
                    angle = 45,
                    legend.pos = "bottom.right") + 
                    scale_x_discrete(labels = c("Overall effect")) + 
                    theme(legend.direction = "horizontal",
                    legend.text = element_text(size = 6)) +
                    
                    scale_colour_okabe_ito()+
                    scale_fill_okabe_ito()

#eyespot vs. conspicuous patterns
p2 <- orchard_plot(mr_eyespot,
                  mod = "Treatment_stimulus",
                  group = "Study_ID",
                  xlab = "log response ratio (lnRR)",
                  angle = 45,
                  legend.pos = "bottom.right") +
                  theme(legend.direction = "horizontal",
                  legend.text = element_text(size = 6)) +
                  scale_colour_okabe_ito(order = 2:3)+
                  scale_fill_okabe_ito(order = 2:3)
                  
# prey type - real vs. artificial
p3 <- orchard_plot(mr_prey_type,
                  mod = "Type_prey",
                  group = "Study_ID",
                  xlab = "log response ratio (lnRR)",
                  angle = 45,
                  legend.pos = "bottom.right") +
                  theme(legend.direction = "horizontal",
                  legend.text = element_text(size = 6))+ 
                  scale_colour_okabe_ito(order = 4:5) +
                  scale_fill_okabe_ito(order = 4:5)

# combine
patch1 <- p1 | (p2 / p3)
patch1 + plot_annotation(tag_levels = "a")

# output figure as pdf
# ggsave("fig1.pdf", width = 10, height = 5, dpi = 450)

```

### Continuous moderators
```{r}
#| label: fig-galary2
#| fig-cap: "Continuous moderators"


# these figs were created by multi meta-regression model results
# log-transformed area
p4 <- bubble_plot(mr_area,
                  mod = "Log_area",
                  group = "Study_ID",
                  xlab = "Log-transformed area") +
                  scale_x_continuous(breaks = seq(0,7,1.5)) +
                  scale_y_continuous(breaks = seq(-2.5, 4.5, 1.5))

# number of patterns
p5 <- bubble_plot(mr_num,
            mod = "Number_pattern",
            group = "Study_ID",
            xlab = "Number of patterns") +
                  scale_x_continuous(breaks = seq(0,11,1.5)) +
                  scale_y_continuous(breaks = seq(-2.5, 4.5, 1.5))

# combine
p4 / p5 + plot_annotation(tag_levels = "a")

# output figure as pdf
ggsave("fig2_multi.pdf", dpi = 450, units = "mm")
```

### Publication bias

```{r}
#| label: fig-galary3
#| fig-cap: "Publication bias"
#| fig-subcap:
#|    - "Funnel plot"
#|    - "Egger's test and Decline effect"
#| layout-ncol: 2

# funnel plot

# pdf("fig3.pdf")

funnel(ma_all, yaxis = "seinv", 
      xlab = "Standarised residuals",
      ylab = "Precision (inverse of SE)",
      xlim = c(-4.0, 4.5), 
      ylim = c(0.01, 80.0), 
      col = c(alpha("mediumvioletred", 0.5)),
      cex = 0.7)

# dev.off()

# Egger's test and decline effect
p7 <- bubble_plot(bias_model,
            mod = "sqrt_inv_e_n",
            group = "Study_ID",
            xlab = "Square root of inverse of effective sample size") +
            scale_y_continuous(breaks = seq(-2.5, 4.5, 1.5)) 

p8 <- bubble_plot(year_model,
            mod = "Year",
            group = "Study_ID",
            xlab = "Year of publication") +  scale_y_continuous(breaks = seq(-2.5, 4.0, 1.5)) 

# combine plots created by bubble_plot()
pub <- p7 / p8
pub +  plot_annotation(tag_levels = 'a') 

# output figure as pdf
# ggsave("fig4.pdf", width = 10, height = 10, dpi = 450)

```
:::

# R session infomation
```{r}
#| echo: false

sessionInfo() %>% pander::pander()

```


